Non-word repetition in Yélî Dnye

### 2020-06-11 manuscript.Rmd
finished integration frequency but bugs remain with some segs having freq na

@@

- double check demo: exact age missing: 78, 82, 83, 115, 119; rough age missing 78, there's a mixture of BGMF in sex, first born is missing, round age
- add frequency of sounds in stimuli in segments.xlsx from https://phoible.org/parameters
- then add that in stimuli to get minimum & average frequencies per stimulus
- then add analysis of NWR as a function of frequency
- draft discussion

@@

- look through for **mc**
- consent, "correct", "accuracy", "performance"
- help with table 1 (formatting)

>>>>

<!-- REMEMBER!!!! -->
<!-- phonetic characters: -->
<!-- - save excel as utf with save as -->
<!-- - do $ iconv -f utf-16le -t utf-8 stimuli.txt > stimconv.txt -->
<!-- - do $ iconv -f utf-16le -t utf-8 segments.txt > segconv.txt -->

@@

- double check demo: exact age missing: 78, 82, 83, 115, 119; rough age missing 78, there's a mixture of BGMF in sex, first born is missing, round age
- then add analysis of NWR as a function of frequency
- draft discussion
- draft abstract

@@

- look through for **mc**
- double check my frequency entries in segments.xlsx using the search function in https://phoible.org/parameters; take a look at http://phoible.github.io/conventions/ in case you see something about double articulation (I didn't find tp or lBj)
- double check phonological implementation of stimuli in stimuli.xlsx 
- for both of the above, if you make any changes, they need to be re-saved as UTF16 txt file, and then converted (see remember above)
- double check also stim_seg_freq -- why are some items still with NA freq?
- consent, "correct", "accuracy", "performance"
- help with table 1 (formatting & making it appear, because it's broken by the phonological representations)
